Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2020-01-03 manuscript/main.tex
Clarify data sources in intro

\begin{figure*}[p]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/test-of-best-model-for-simulated-populations.png}
  \caption{
  Test of best model for simulated populations (true fitness) using 9 years previously unobserved test data and fixed model coefficients.
  A) The correlation of log estimated clade growth ratio, $\log_{10}{\frac{\hat{x}(t + \Delta{t})}{x(t)}}$, and log observed clade growth ratio, $\log_{10}{\frac{x(t + \Delta{t})}{x(t)}}$, shows the model's ability to capture clade-level dynamics without explicitly optimizing for clade frequency targets.
  B) The rank of the estimated best strain based on its distance to the future in the best model for 18 timepoints shows how often the model makes a good choice when forced to select a single representative strain for the future population.
  The estimated best strain was in the top 20th percentile of observed closest strains for 89\% of timepoints, confirming that the model makes a good choice when forced to select a single representative strain for the future population.
  C) Absolute forecast error for clades shown in A by their initial frequency with a mean LOESS fit (solid black line) and 95\% confidence intervals (gray shading) based on 100 bootstraps.
  D) The correlation of all strains at all timepoints by the percentile rank of their observed and estimated distances to the future.
  }
  \label{fig:test_of_best_model_for_simulated_populations}
  \end{center}
\end{figure*}

>>>>

\begin{figure*}[p]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/test-of-best-model-for-simulated-populations.png}
  \caption{
  Test of best model for simulated populations (true fitness) using 9 years previously unobserved test data and fixed model coefficients.
  A) The correlation of log estimated clade growth ratio, $\log_{10}{\frac{\hat{x}(t + \Delta{t})}{x(t)}}$, and log observed clade growth ratio, $\log_{10}{\frac{x(t + \Delta{t})}{x(t)}}$, shows the model's ability to capture clade-level dynamics without explicitly optimizing for clade frequency targets.
  B) The rank of the estimated best strain based on its distance to the future in the best model for 18 timepoints shows how often the model makes a good choice when forced to select a single representative strain for the future population.
  The estimated best strain was in the top 20th percentile of observed closest strains for 89\% of timepoints, confirming that the model makes a good choice when forced to select a single representative strain for the future population.
  C) Absolute forecast error for clades shown in A by their initial frequency with a mean LOESS fit (solid black line) and 95\% confidence intervals (gray shading) based on 100 bootstraps.
  \rnc{it would be interesting to look at this for neg and pos deviations separately.}
  D) The correlation of all strains at all timepoints by the percentile rank of their observed and estimated distances to the future.
  }
  \label{fig:test_of_best_model_for_simulated_populations}
  \end{center}
\end{figure*}
